\bf Excuse me, do you have a moment to talk about version control?

### 2017-06-30 README.Rmd
Work on branches and pull requests

Branches and pull requests are an extremely powerful feature of Git/GitHub and should be your first foray beyond the basics of commit, push, and pull. A branch is an independent line of development within a repo, with the notion it will eventually be merged back into the main branch, a.k.a. "master". In a course website, you might work in a branch to update a series of lessons, while leaving the current version intact in the meantime. A pull request is a specific and formal GitHub process for merging one branch into another. You can make a pull request between two branches in the same repo or between two copies of a repo. This is the mechanism for making and accepting contributions to open source software projects on GitHub, including many popular R packages *link to a search?*.

>>>>

Branches and pull requests are an extremely powerful feature of Git/GitHub and should be your first foray beyond the basics of commit, push, and pull. A branch is an independent line of development within a repo, where the intent is usually to merge it into the master branch when ready. In a course website, you might work in a branch to update a series of lessons, while leaving the current version intact in the meantime. A pull request is a GitHub-specific way to propose changes to a repo that augments Git's regular branch and merge workflow with facilities for structured review. A pull request can be made between two branches in the same repo, such as `master` and `bugfix`, or between two independent copies of a repo, an original and a so-called "fork". This is the mechanism for making and accepting contributions to open source software projects on GitHub, including many popular R packages *link to a search?*.

### 2017-06-30 README.tex
Work on branches and pull requests

Branches and pull requests are an extremely powerful feature of
Git/GitHub and should be your first foray beyond the basics of commit,
push, and pull. A branch is an independent line of development within a
repo, with the notion it will eventually be merged back into the main
branch, a.k.a. ``master''. In a course website, you might work in a
branch to update a series of lessons, while leaving the current version
intact in the meantime. A pull request is a specific and formal GitHub
process for merging one branch into another. You can make a pull request
between two branches in the same repo or between two copies of a repo.
This is the mechanism for making and accepting contributions to open
source software projects on GitHub, including many popular R packages
\emph{link to a search?}.

>>>>

Branches and pull requests are an extremely powerful feature of
Git/GitHub and should be your first foray beyond the basics of commit,
push, and pull. A branch is an independent line of development within a
repo, where the intent is usually to merge it into the master branch
when ready. In a course website, you might work in a branch to update a
series of lessons, while leaving the current version intact in the
meantime. A pull request is a GitHub-specific way to propose changes to
a repo that augments Git's regular branch and merge workflow with
facilities for structured review. A pull request can be made between two
branches in the same repo, such as \texttt{master} and \texttt{bugfix},
or between two independent copies of a repo, an original and a so-called
``fork''. This is the mechanism for making and accepting contributions
to open source software projects on GitHub, including many popular R
packages \emph{link to a search?}.
